Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-07-10 thirdPaper/draft/typeConeAssociahedra.tex
Comment on Proposition 2.34 (ii) in answer to Arnau's comment.
corrected a typo and removed a comment

\noindent \cref{prop:exchangeablePairsNKC} (ii): \emph{The non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.}
\arnau{In the proof of \cref{prop:exchangeablePairsNKC} it says that the UERP follows from PPP17}
\medskip

@@

In \cref{sec:clusterCategories}, we prove an analogue for cluster categories of a result of M. Auslander for module categories of Artin algebras~\cite{Auslander1984}. \arnau{Which result? Is it famous? Should we say something like Auslaunder's famous result from...? }\pg{I've reformulated slightly.  Auslander was extremely prolific :-)}
We are mainly motivated by the fact that it has for a consequence that the type cones of the cluster fans of finite type are simplicial.
However, this result is of independent interest and sheds new lights on the Grothendieck groups of cluster categories.

@@

% Schematic diagram:
\yann{Vincent, Arnau, je suis certain que vous feriez bien mieux que moi. Puis-je vous demander de le représenter ?}
\arnau{As tu une idée en tête de comment le réprsenter? Je trouve que ce que t'as écrit est très clair et je ne vois pas comment faire une schema qui le ameillore}
% 
% I.1 explains the type cone approach to the problem
% 
% This strategy is used in I.2.2 for cluster algebras and in I.2.3 for gentle algebras.
% 
% II.3 cluster categories (2-Calabi--Yau triangulated categories) is used in 1.2.2 for proving U.E.R.P. and simpliciality of the type cone.
% 
% II.4 generalises II.3, is used in I.2.3 for proving the U.E.R.P. and offers a different proof of simpliciality of the type cone .

@@

\begin{proof}
Points~(i), (iii) and~(iv) where shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon-nonkissing}. We postpone the proof of point~(ii) until \cref{coro::exchangeablePairsNKC}.
\end{proof}

>>>>

\noindent \cref{prop:exchangeablePairsNKC} (ii): \emph{The non-kissing fan~$\Fan(\quiver)$ has the unique exchange relation property.}
\arnau{In the proof of \cref{prop:exchangeablePairsNKC} it says that the UERP follows from PPP17}\pg{Not for point (ii), which uses results of Section 4}
\medskip

@@

In \cref{sec:clusterCategories}, we prove an analogue for cluster categories of a result of M. Auslander for module categories of Artin algebras~\cite{Auslander1984}. 
We are mainly motivated by the fact that it has for a consequence that the type cones of the cluster fans of finite type are simplicial.
However, this result is of independent interest and sheds new lights on the Grothendieck groups of cluster categories.

@@

% Schematic diagram:
\yann{Vincent, Arnau, je suis certain que vous feriez bien mieux que moi. Puis-je vous demander de le représenter ?}
\arnau{As tu une idée en tête de comment le répresenter? Je trouve que ce que t'as écrit est très clair et je ne vois pas comment faire une schema qui le ameillore}
% 
% I.1 explains the type cone approach to the problem
% 
% This strategy is used in I.2.2 for cluster algebras and in I.2.3 for gentle algebras.
% 
% II.3 cluster categories (2-Calabi--Yau triangulated categories) is used in 1.2.2 for proving U.E.R.P. and simpliciality of the type cone.
% 
% II.4 generalises II.3, is used in I.2.3 for proving the U.E.R.P. and offers a different proof of simpliciality of the type cone .

@@

\begin{proof}
Points~(i), (iii) and~(iv) were shown in~\cite[Prop.~2.33, Thm.~4.17 \& Prop~4.16]{PaluPilaudPlamondon-nonkissing}. We postpone the proof of point~(ii) until \cref{coro::exchangeablePairsNKC}.
\end{proof}
